---
title: "Find a perfect place"
author: "iDash team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Let's find the best place for you in Amsterdam!

## Importing data

First, we have to import data from http://insideairbnb.com webpage. To do that, run `download_airbnb_data()` function:

```{r, eval=F}
download_airbnb_data(data_to_load = c("listings", "calendar"), 
                     city = "Amsterdam", 
                     format = "raw")
```

It gives us two files: `*listings.csv` with information about each rented flat in Amsterdam and `*calendar.csv` which stores info about flat availability year ahead. The argument `format = "raw"` indicates we only want to import raw data.

## Search component

So we'd like to find a place:

- for 3 nights, 
- for 2 people, 
- checkin will be at `"2019-01-30"`,    
- with price ranged between 50\$ and 150\$ per night,   
- at most 2 kilometers from the city center.    

Also we're interested only in places with rating higher than 95 points.

### First approach

We can do it by building a pipeline.


```{r,eval = F}
library(dplyr)
listings <- readr::read_csv("airbnb_data/amsterdam20181206listings.csv.gz")
calendar <- readr::read_csv("airbnb_data/amsterdam20181206calendar.csv.gz")

best_flats_df <- listings %>% 
    find_located_flat(distance_center, distance = 2) %>%
    find_reviewed_flat(bayes_review) %>%
    find_priced_flat(num_guests = 2, price = c(50, 150)) %>%
    find_available_flat(calendar, checkin = "2019/01/30", num_days = 3)
```

### Second approach

We can also use `find_your_place` function which is a wrapper of the pipeline.

```{r,eval = F}
best_flats_df <- find_your_place(listings, calendar, checkin = "2019/01/30", 
                                 num_days = 3, num_guests = 2, distance = 2, 
                                 price = c(50, 150))
```


## Show the best options

We can generate the map with our best options. All we have to do is to run `show_your_place` function.

```{r, eval = F}
show_your_place(best_flats_df, top = 5)
```

